---
title: "Weight of Fish"
author: "Nathan Abromovich"
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 5
  pdf_document:
    toc: yes
    toc_depth: '5'
---


```{r}
require(tigerstats)
require(tidyverse)
```


# Predicting Fish Weight

```{r}
Fish <-read_csv(file="Fish.csv")
Perch <-filter(Fish, Species=="Perch")
Perch <-select(Perch,-Species)

```



## Perch


### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
```{r}
MODLPerch <- lm(Weight~ .-Weight-Length1-Length2-Length3 ,data=Perch)
summary.lm(MODLPerch)
```
### Best Two regressor model
The model that uses Height and Width.  When using this model we get a adjusted R-squared of 0.94 

## Pike
```{r}
Pike <- filter (Fish,Species=="Pike")
Pike <-select(Pike,-Species)
```
### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
### Best Two regressor model
The best model for the Pike is the model that contains Length 1 and Length 2. 


## Roach
```{r}
Roach <- filter (Fish,Species=="Roach")
Roach <-select(Roach,-Species)
```
### Best Models
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")

```
```{r}
MODLRoach <- lm(Weight~ .-Weight-Length1-Length2-Height ,data=Perch)
summary.lm(MODLRoach)
```

### Best Two regressor model
For the Roach fish the model that contains the Length 3 and Width data was the best model to use.  When using the model we get a high adjusted R-squared value of 0.9346.



## Final Summary Statements